---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev.args = list(png = list(type = "cairo")),
  echo = TRUE,
  dpi = 150, 
  fig.align = "center")
```

# aqua - <ins>a</ins>ssay <ins>qua</ins>lification and validation tools

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/dmarginean/aqua?branch=master&svg=true)](https://ci.appveyor.com/project/dmarginean/aqua)
<!-- badges: end -->

The (future, long term, eventual) goal of aqua is to provide tools that help with different assay qualification and validation project analysis and reporting.

## Installation

You can install aqua. I hope. You're on your own.

``` r
devtools::install_github("cgtc/aqua")    # fingers crossed
```

## Examples

```{r example}
library(aqua)

sd(c(2,3,2))   # boring
sd.u(c(2,3,2)) # amazing
```

`sd.u` produces a very unbiased standard deviation estimate. Makes every small sample size data look horrible. The sad but true reality. Uses a chi-distributed correction factor.


```{r example2}
library(lme4)

funky_model <- lmer(total.fruits ~ 1 + (1|amd) + (1|status), data = Arabidopsis)

get_intermed_levels(funky_model) %>%
  knitr::kable(escape = F) %>%
  kable_style()

```

Boom. Clearly the contribution of `amd` and `status` to variations in `fruit.growth` (in a vacuum) in this model I just invented that makes no sense is what it says there.

You can get repeatability and overall intermediate precision / reproducibility of an assay if you turned it into an lme4 random model with the only fixed term being an intercept. Just describe your model like `1 + (1|Lab/Operator/Day) + (1|SampleType)` or whatever your assay design structure is and fire it up. 

You can also do the whole TCID50 assay calculations. There's a lot of functions for that that tend to even work! Does anyone use TCID50 anymore? Hello?

## Version

Currently 0.1 MEGA ALPHA
